---
title: "hailr installation"
author: "Samuel Macêdo"
date: "April 19, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### walkthrough

1) fork the repo <https://github.com/lawremi/hailr> and create a project   
2) install BiocManager and devtools on CRAN

```{r, eval = FALSE}
install.packages("BiocManager")
install.packages("devtools")
```

3) install the dependecies in this order

```{R, eval = FALSE}
BiocManager::install("IRanges")
BiocManager::install("GenomicRanges")
BiocManager::install("BiocParallel")
BiocManager::install("SummarizedExperiment")
devtools::install_github("Bioconductor/S4Vectors")
```

### some notes
1) The `BioGenerics` package doesn't build in R 3.5, but when you install `IRanges` first `BioGenerics` works fine. That's why `IRanges` comes first.

2) `BiocParallel` doesn't appear in the dependencies, but it is required to build `SummarizedExperiment`.

3) `hailr` requires a `S4Vectors` version greater than the version in Bioconductor repository. You need to install the dev version on GitHub.