---
title: "Programming Hail with R: A Tutorial"
author: "Michael Lawrence"
package: hailr
date: "`r Sys.Date()`"
output:
  BiocStyle::html_document:
    toc_float: true
vignette: >
  %\VignetteIndexEntry{Tutorial}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

# Introduction

## The hailr package

The hailr package is an interface between R and Hail, a platform for
genomic computing on Spark, a distributed computing system. The goal
of the package is to model data inside of Hail as if it were stored in
conventional Bioconductor data structures like SummarizedExperiment,
GRanges, DataFrame, etc. It implements the API for those data
structures on top of Hail, so the data stay in Hail (as long as it
makes sense), and Hail/Spark are able to distribute computations
across the available compute resources.

```{r}
library(hailr)
```

## The Data

We are using a subset of the 1000 Genomes data, on about 10,000
positions, along with some sample annotations with invented
phenotypes, as provided by the Hail tutorial
(https://hail.is/docs/stable/tutorials/hail-overview.html).

## Setup

The hailr package will automatically ensure that Hail is installed and
configured for this demonstration. To use a system installation of
Hail, see `?use_hail_home`.

# HailExperiment: Central Interface to Hail

The HailExperiment object is a derivative of SummarizedExperiment that
is based on the Hail MatrixTable data type, which has a very similar
structure.

The data are stored as a VDS file within the hailr package. We load
the VDS file as a HailExperiment:

```{r}
vcf <- system.file("extdata", "1kg.vcf.bgz", package="hailr")
#he <- readHailExperimentFromVCF(vcf, genome="GRCh37")
```
